Chemical potential of liquids and mixtures via Adaptive Resolution Simulation

### 2014-05-20 writeDown/pub.jcp/chem-pot-jcp.tex
update the values in the table. change small things

In Ref.~\cite{prx} it has been shown that the chemical potential of the atomistic and coarse-grained resolution are related by the following formula: 
\begin{equation}
\mu_{\CG}=\mu_{\AT}+\omega_{\thf}+\omega_{\thermo}
\label{mu}
\end{equation}
with $\mu_{\CG}$ the chemical potential of the coarse-grained system (in GC-AdResS this corresponds to a liquid of generic spheres), $\mu_{\AT}$  the chemical potential of the atomistic system, $\omega_{\thf}=\int_{\Delta}{\vect F}_{\thf}({\vect r})d{\vect r}$ the work of the thermodynamic force in the transition region, $\omega_{\thermo}$ the work/heat provided by the thermostat in order to slowly equilibrate the inserted/removed degrees of freedom in the transition region. $\omega_{\thermo}$ is composed by two parts, one, called $\omega_{\ext}$, which compensates the dissipation of energy due to the non-conservative interactions in $\Delta$, and another, $\omega_{\dof}$, which is related to the equilibration of the reinserted/removed degrees of freedom (rotational and vibrational). \recheck{While the determination of $\omega_{\dof}$ is not required for our final aim (that is the calculation of the excess chemical potential, as explained later on), the calculation of $\omega_{\thermo}$ is very relevant}. However this calculation is not straightforward and we have proposed to introduce an auxiliary Hamiltonian approach where the coarse-grained and atomistic potential are interpolated, and not the forces as in \recheck{the original} AdResS. Next, we impose that the Hamiltonian system must have the same thermodynamic equilibrium of the original force-based GC-AdResS system; this is done by introducing a thermodynamic force in the auxiliary Hamiltonian approach, which, at the target temperature, keeps the density of particles across the system as in GC-AdResS. \recheck{In the auxiliary Hamiltonian approach we have the same equilibrium as the original adaptive (and full atomistic) system  and the difference between the work of the original thermodynamic force and the work of the thermodynamic force calculated in the Hamiltonian approach gives $\omega_{\ext}$ (further details about this point are given in the {Appendix~\ref{app:tmp2}})}. Moreover we have proven numerically, for the case of liquid water, that
  $\omega_{\ext}=\int_{\Delta}\nabla w(\vect r)\langle w( U^{\AT}-U^{\CG})\rangle_{\vect r} d{\vect r}$,
  where $U_{\AT}$ and $U_{\CG}$ are the atomistic and coarse-grained potential.
\recheck{It must be noticed that the auxiliary Hamiltonian approach shall not be considered a Hamiltonian approach to adaptive resolution simulation. In fact, as discussed in Ref.\cite{prx} the equilibrium is imposed artificially and {\it per se} does not have any physical meaning (for more details, see discussion in the {Appendix~\ref{app:tmp2}})}. 
\recheck{In the next section of this work we show analytically that the formula above is exact (at least) at the first order w.r.t. the probability distribution of the system as defined in Eq.\ref{order}}.\\

The result above implies that $\omega_{\thermo}$ can be calculated in a straightforward way during the initial equilibration within in the standard GC-AdResS code. 
\recheck{It must be noticed that, within the AdResS scheme, an approach similar to the auxiliary Hamiltonian  has been recently proposed and applied to liquids and mixtures (of toy models so far) by Potestio {\it et al.} \cite{h-adress-0, h-adress} (see also \cite{luigientropy} where such an approach is commented)}. At this point according to \eqref{mu}, if one knows $\mu_{\CG}$, then  GC-AdResS can automatically provide $\mu_{\AT}$. However we need to do one step more, in fact the quantity of interest is not the total chemical potential, but the excess chemical potential $\mu^{\exc}_{\AT}$ which corresponds to the expression of \eqref{mu} where the kinetic (ideal gas) part is subtracted. Regarding the kinetic part, one can notice that the contribution coming from the COM is the same for the coarse-grained and for the atomistic molecules, thus it is automatically removed in the calculation of \eqref{mu}.
The kinetic part of $\mu_{\AT}$ due to the rotational and vibrational degrees of freedom corresponds in our case to $\omega_{\dof}$ and \recheck{in principle can be calculated by hand (chemical potential of an isolated molecules). However such a calculation may become rather tedious for large and/or complex molecules but in our case it is actually not required.} In fact the \recheck{Gromacs implementation of AdResS} considers the removed degrees of freedom as phantom variables but thermally equilibrate them anyway~\cite{simon-ch}. Thus the heat provided by the thermostat for the rotational and vibrational part is the same in the atomistic and coarse-graining molecules and is automatically removed in the difference. Finally, the calculation of $\mu^{\exc}_{\CG}$ can be done with standard methods, TI or IPM, which for simple spherical molecules, like those of the coarse-grained system, requires a negligible computational cost.
In conclusion, we have the final expression:
\begin{equation}
  \mu^{\exc}_{\AT}=
  \mu^{\exc}_{\CG}-
  \int_{\Delta}{F}_{th}({\vect r})d{\vect r}-
  \int_{\Delta}\nabla_{\vect r} w(\vect r) \langle w(U^{\AT}-U^{\CG})\rangle_{\vect r} d{\vect r}
\label{finalmu}
\end{equation}

@@

\begin{table}[]
\begin{center}
%\begin{tabular}{ccccc}
\begin{tabular}{ccccc}
\hline \hline
 Liquid component & Mole fraction of solute & GC-AdResS & TI & Experiment \\
\hline
\recheck{water} & -- & -22.1 $\pm$ 0.2  & -- & -23.5 \cite{florian} \\
methane  & -- & -4.6 $\pm$ 0.1  & -5.2 $\pm$ 0.1 & -- \\
ethane   & -- & -8.2 $\pm$ 0.3  &  -8.8 $\pm$ 0.1 & -- \\
propane  & -- & -8.5 $\pm$ 0.1 & -9.5 $\pm$ 0.2 & -- \\
\recheck{methanol}  & -- & -20.3 $\pm$ 0.2 & -20.9 $\pm$ 0.3 & -20.5 \cite{vang}  \\
DMSO & -- & -32.2 $\pm$ 0.3 & -34.7 $\pm$ 0.7 & -32.2 \cite{dmso}  \\
\recheck{methanol in methanol/water mixture} & 0.01 & -19.0 $\pm$ 0.2 & -- & -- \\
\recheck{methane in methane/water mixture} & 0.006 & 9.3 $\pm$ 0.2  & -- & -- \\
urea in urea/water mixture & 0.02 & -56.1 $\pm$ 0.6 & -58.2 $\pm$ 0.5 & -57.8 $\pm$ 2.5 \cite{urea} \\
\recheck{ethane in ethane/water mixture} & 0.006 & 7.2 $\pm$ 0.2 & -- & -- \\ 
\recheck{TBA in water/TBA mixture} & 0.001 & -19.5 $\pm$ 0.5 & -20.8 $\pm$ 0.6 & -19.0 \cite{nico} \\
DMSO in DMSO/water mixture & 0.01 & -31.4 $\pm$ 0.5 & -33.2 $\pm$ 0.3 & -- \\
TBA in TBA/DMSO mixture & 0.02 & -24.8 $\pm$ 0.4 & -24.0 $\pm$ 0.5 & -- \\
\hline \hline
\end{tabular}
\caption{The excess chemical potential of different liquids and mixtures in kJ/mol calculated from GC-AdResS and TI of full atomistic simulations. Experimental values for systems at the same concentrations used in simulation are also reported for comparison. For pure systems (water and methanol) we compare our values with those obtained in literature using the same force field and computational code. For mixtures, most of the values from literature (simulation and experiments) are available at lower concentrations (see Refs.\cite{vang,nico}); However, since we are always in a very dilute regime the chemical potential does not change significantly. \recheck{We have provided evidence for the TBA/water misture that such consistency holds (see Fig.\ref{concentration})}. Note that the chemical potential of water in dilute mixtures is the same of pure water and is not reported above.
}
\label{table}
\end{center}
\end{table}

@@

\recheck{In order to show the numerical efficiency of our approach, we compare the time taken to do a full GC-AdResS simulation and the time for a thermodynamic integration calculation for
different systems with varied concentration of TBA in water. The total time required for an GC-AdResS simulation consists of 
the time taken to obtain a converged thermodynamic force and the time taken to obtain the coarse-grained chemical potential. 
The time taken to complete TI procedure at each value of $\lambda$ is summed up to obtain the total time. In this work, the TI 
is done in two stages, first the van der Waals  interactions are coupled followed by the electrostatic coupling. At each stage, 21 
equally distributed values of $\lambda$ are used,
therefore, in total 42 simulations were performed to calculate each TI chemical potential value.
% However, in literature, a single stage procedure which consists of coupling 
%  van der Waals and electrostatic interactions together is followed. In order to have a fair comparison, we have compared GC-AdResS time
% to the single-stage TI procedure. Also, GC-AdResS calculations have been done in a more optimized way, by using a spherical atomistic region and 
% a transition region of $1.4 nm$ each. 
In an AdResS simulation, the initial guess of the thermodynamic force largely determines the time for convergence. 
We started with a randomly chosen initial guess
($-42$~kJ/mol, we picked a very small value because the TBA molecule is highly hydrophilic)
for system with the highest mole fraction of TBA. For all the other systems, 
we used the converged thermodynamic force obtained from the first system as an initial guess. The convergence was much 
faster in all the other cases using this approach. Table~\ref{table3} shows the number of iterations required for 
the thermodynamic force convergence in GC-AdResS and total time required for GC-AdResS and TI calculation.
% The total time for the all the calculations is 66 hours in GC-AdResS and 72 hours in TI.
The advantage of GC-AdResS over TI
is that we get two values of excess chemical potential for both solute and solvent in a single calculation, while 
in TI, the whole process has to be repeated to get the excess chemical potential of other component. For very dilute systems ($\concenttba=0.001$), 
however, one has to take a very large systems in GC-AdResS (see the Appendix~\ref{app:tmp1} for system size). It takes a large amount of time for the thermodynamic force to reach convergence, and hence TI is always a better option at such low concentrations with a much 
smaller system size at the same mole fraction.

@@

In all the AdResS simulations, 30 iterations were performed to obtain a 
converged thermodynamic force and a flat density profile. Each iteration consisted 
of 200 ps of equilibration which was followed by 200 ps of data collection. 
The simulations were performed at NVT conditions where the temperature was kept constant 
at 298 K. Simulations of liquid methane and ethane were performed at
111.66 K and 184.52 K respectively. \recheck{As it was discussed in~\cite{prx}, there is no requirement 
of a coarse-grained model that resembles the structural and thermodynamic properties of a full atomistic
model. It was shown numerically that the proper exchange of energy and molecules was independent from the 
molecular model used in the coarse-grained region, showing the convenience of GC-AdResS. In this work, a generic WCA potential was used in the 
coarse-grained region. The interaction potential between the coarse-grained particles is given by 
\begin{equation}
  U(r) = 4 \epsilon \left[\left(\frac{\sigma}{r}\right)^{12} - \left(\frac{\sigma}{r}\right)^{6}\right] + \epsilon,
  \quad
  r \leq 2^{1/6}\sigma. 
\end{equation}
The parameters $\sigma$ and $\epsilon$ were chosen such that the radial distribution functions of particles 
reproduce a liquid structure. For water molecule, the parameters used in this study are $\epsilon=0.65$~kJ/mol
and $\sigma=0.30$~nm. Table~\ref{cg} shows the WCA parameters for other molecules used in this work.
For interactions between solute and solvent, $\sigma$ values were obtained by 
averaging over the individual parameters.
The solute-solvent $\epsilon$ is the same as the solute-solute  $\epsilon$.
\\
}

@@

In all the simulations, a leap-frog stochastic dynamics integrator with a time step
of 2~fs and an inverse friction coefficient of 0.1~ps was used. All bond-lengths were constrained using the LINCS 
algorithm. \recheck{As discussed previously, a higher cut-off radius of $1.4$~nm has been used for van der Waals and Coulomb interactions,
in AdResS and full-atom simulations}. 
Electrostatic interactions beyond the cut-off radius were calculated using the reaction-field term \cite{rf} with a dielectric 
permittivity of 54 for urea in SPC water \cite{urea}, 64.8 for TBA in SPC water \cite{nico}, 61 for other solutes in SPC
water, 19 for methanol and 46 for DMSO as the solvent \cite{vang}.

>>>>

In Ref.~\cite{prx} it has been shown that the chemical potential of the atomistic and coarse-grained resolution are related by the following formula: 
\mu_{\CG}=\mu_{\AT}+\omega_{\thf}+\omega_{\thermo}
\label{mu}
with $\mu_{\CG}$ the chemical potential of the coarse-grained system (in GC-AdResS this corresponds to a liquid of generic spheres), $\mu_{\AT}$  the chemical potential of the atomistic system, $\omega_{\thf}=\int_{\Delta}{\vect F}_{\thf}({\vect r})d{\vect r}$ the work of the thermodynamic force in the transition region, $\omega_{\thermo}$ the work/heat provided by the thermostat in order to slowly equilibrate the inserted/removed degrees of freedom in the transition region. $\omega_{\thermo}$ is composed by two parts, one, called $\omega_{\ext}$, which compensates the dissipation of energy due to the non-conservative interactions in $\Delta$, and another, $\omega_{\dof}$, which is related to the equilibration of the reinserted/removed degrees of freedom (rotational and vibrational). \recheck{While the determination of $\omega_{\dof}$ is not required for our final aim (that is the calculation of the excess chemical potential, as explained later on), the calculation of $\omega_{\thermo}$ is very relevant}. However this calculation is not straightforward and we have proposed to introduce an auxiliary Hamiltonian approach where the coarse-grained and atomistic potential are interpolated, and not the forces as in \recheck{the original} AdResS. Next, we impose that the Hamiltonian system must have the same thermodynamic equilibrium of the original force-based GC-AdResS system; this is done by introducing a thermodynamic force in the auxiliary Hamiltonian approach, which, at the target temperature, keeps the density of particles across the system as in GC-AdResS. \recheck{In the auxiliary Hamiltonian approach we have the same equilibrium as the original adaptive (and full atomistic) system  and the difference between the work of the original thermodynamic force and the work of the thermodynamic force calculated in the Hamiltonian approach gives $\omega_{\ext}$ (further details about this point are given in the {Appendix~\ref{app:tmp2}})}. Moreover we have proven numerically, for the case of liquid water, that
  $\omega_{\ext}=\int_{\Delta}\nabla w(\vect r)\langle w( U^{\AT}-U^{\CG})\rangle_{\vect r} d{\vect r}$,
  where $U_{\AT}$ and $U_{\CG}$ are the atomistic and coarse-grained potential.
\recheck{It must be noticed that the auxiliary Hamiltonian approach shall not be considered a Hamiltonian approach to adaptive resolution simulation. In fact, as discussed in Ref.\cite{prx} the equilibrium is imposed artificially and {\it per se} does not have any physical meaning (for more details, see discussion in the {Appendix~\ref{app:tmp2}})}. 
\recheck{In the next section of this work we show analytically that the formula above is exact (at least) at the first order w.r.t. the probability distribution of the system as defined in Eq.\ref{order}}.
The result above implies that $\omega_{\thermo}$ can be calculated in a straightforward way during the initial equilibration within in the standard GC-AdResS code. 
\recheck{It must be noticed that, within the AdResS scheme, an approach similar to the auxiliary Hamiltonian  has been recently proposed and applied to liquids and mixtures (of toy models so far) by Potestio {\it et al.} \cite{h-adress-0, h-adress} (see also \cite{luigientropy} where such an approach is commented)}. At this point according to \eqref{mu}, if one knows $\mu_{\CG}$, then  GC-AdResS can automatically provide $\mu_{\AT}$. However we need to do one step more, in fact the quantity of interest is not the total chemical potential, but the excess chemical potential $\mu^{\exc}_{\AT}$ which corresponds to the expression of \eqref{mu} where the kinetic (ideal gas) part is subtracted. Regarding the kinetic part, one can notice that the contribution coming from the COM is the same for the coarse-grained and for the atomistic molecules, thus it is automatically removed in the calculation of \eqref{mu}.
The kinetic part of $\mu_{\AT}$ due to the rotational and vibrational degrees of freedom corresponds in our case to $\omega_{\dof}$ and \recheck{in principle can be calculated by hand (chemical potential of an isolated molecules). However such a calculation may become rather tedious for large and/or complex molecules but in our case it is actually not required.} In fact the \recheck{Gromacs implementation of AdResS} considers the removed degrees of freedom as phantom variables but thermally equilibrate them anyway~\cite{simon-ch}. Thus the heat provided by the thermostat for the rotational and vibrational part is the same in the atomistic and coarse-graining molecules and is automatically removed in the difference. Finally, the calculation of $\mu^{\exc}_{\CG}$ can be done with standard methods, TI or IPM, which for simple spherical molecules, like those of the coarse-grained system, requires a negligible computational cost.
In conclusion, we have the final expression:
  \mu^{\exc}_{\AT}=
  \mu^{\exc}_{\CG}-
  \int_{\Delta}{F}_{th}({\vect r})d{\vect r}-
  \int_{\Delta}\nabla_{\vect r} w(\vect r) \langle w(U^{\AT}-U^{\CG})\rangle_{\vect r} d{\vect r}
\label{finalmu}

@@

\begin{table}[]
\begin{center}
%\begin{tabular}{ccccc}
\begin{tabular}{ccrrc}
\hline \hline
 Liquid component & Mole fraction of solute & GC-AdResS & TI & Experiment \\
\hline
\recheck{water} & -- & $-23.9 \pm 0.3$  & $-22.3 \pm 0.6$ & $-23.5$~\cite{florian} \\
methane  & -- & $-4.6 \pm 0.1$  & $-5.2 \pm 0.1$ & -- \\
ethane   & -- & $-8.2 \pm 0.3$  & $-8.8 \pm 0.1$ & -- \\
propane  & -- & $-8.5 \pm 0.1$ & $-9.5 \pm 0.2$ & -- \\
\recheck{methanol}  & -- & $-20.3 \pm 0.2$ & $-20.9 \pm 0.3$ & $-20.5$ \cite{vang}  \\
DMSO & -- & $-32.2 \pm 0.3$ & $-34.7 \pm 0.7$ & $-32.2$ \cite{dmso}  \\
\recheck{methanol in methanol/water mixture} & 0.01 & $-19.0 \pm 0.2$ & $-19.7 \pm 0.2$ & -- \\
\recheck{methane in methane/water mixture} & 0.006 & $9.3 \pm 0.2$  & $8.2 \pm 0.3$ & -- \\
urea in urea/water mixture & 0.02 & $-56.1 \pm 0.6$ & $-58.2 \pm 0.5$ & $-57.8 \pm 2.5$ \cite{urea} \\
\recheck{ethane in ethane/water mixture} & 0.006 & $7.2 \pm 0.2$ & $7.3 \pm 0.3$ & -- \\ 
\recheck{TBA in water/TBA mixture} & 0.001 & $-19.5 \pm 0.5$ & $-20.8 \pm 0.6$ & $-19.0$ \cite{nico} \\
DMSO in DMSO/water mixture & 0.01 & $-31.4 \pm 0.5$ & $-33.2 \pm 0.3$ & -- \\
TBA in TBA/DMSO mixture & 0.02 & $-24.8 \pm 0.4$ & $-24.0 \pm 0.5$ & -- \\
\hline \hline
\end{tabular}
\caption{The excess chemical potential of different liquids and mixtures in kJ/mol calculated from GC-AdResS and TI of full atomistic simulations. Experimental values for systems at the same concentrations used in simulation are also reported for comparison. For pure systems (water and methanol) we compare our values with those obtained in literature using the same force field and computational code. For mixtures, most of the values from literature (simulation and experiments) are available at lower concentrations (see Refs.\cite{vang,nico}); However, since we are always in a very dilute regime the chemical potential does not change significantly. \recheck{We have provided evidence for the TBA/water misture that such consistency holds (see Fig.\ref{concentration})}. Note that the chemical potential of water in dilute mixtures is the same of pure water and is not reported above.
}
\label{table}
\end{center}
\end{table}

@@

\recheck{In order to show the numerical efficiency of our approach, we compare the time taken to do a full GC-AdResS simulation and the time for a thermodynamic integration calculation for
different systems with varied concentration of TBA in water. The total time required for an GC-AdResS simulation consists of 
the time taken to obtain a converged thermodynamic force and the time taken to obtain the coarse-grained chemical potential. 
The time taken to complete TI procedure at each value of $\lambda$ is summed up to obtain the total time. In this work, the TI 
is done in two stages, first the van der Waals  interactions are coupled followed by the electrostatic coupling. At each stage, 21 
equally distributed values of $\lambda$ are used,
therefore, in total 42 simulations were performed to calculate each TI chemical potential value.
% However, in literature, a single stage procedure which consists of coupling 
%  van der Waals and electrostatic interactions together is followed. In order to have a fair comparison, we have compared GC-AdResS time
% to the single-stage TI procedure. Also, GC-AdResS calculations have been done in a more optimized way, by using a spherical atomistic region and 
% a transition region of $1.4 nm$ each. 
In an AdResS simulation, the initial guess of the thermodynamic force largely determines the time for convergence. 
We started with a randomly chosen initial guess
($-42$~kJ/mol, we picked a small value because the TBA molecule is hydrophilic)
for system with the highest mole fraction of TBA. For all the other systems, 
we used the converged thermodynamic force obtained from the first system as an initial guess. The convergence was much 
faster in all the other cases using this approach. Table~\ref{table3} shows the number of iterations required for 
the thermodynamic force convergence in GC-AdResS and total time required for GC-AdResS and TI calculation.
% The total time for the all the calculations is 66 hours in GC-AdResS and 72 hours in TI.
The advantage of GC-AdResS over TI
is that we get two values of excess chemical potential for both solute and solvent in a single calculation, while 
in TI, the whole process has to be repeated to get the excess chemical potential of other component. For very dilute systems ($\concenttba=0.001$), 
however, one has to take a very large systems in GC-AdResS (see the Appendix~\ref{app:tmp1} for system size). It takes a large amount of time for the thermodynamic force to reach convergence, and hence TI is always a better option at such low concentrations with a much 
smaller system size at the same mole fraction.

@@

In all the AdResS simulations, the resolution changes only on $x$ direction.
For each system, 30 iterations were performed to obtain a 
converged thermodynamic force and a flat density profile. Each iteration consisted 
of 200 ps of equilibration which was followed by 200 ps of data collection. 
The simulations were performed at NVT conditions where the temperature was kept constant 
at 298 K. Simulations of liquid methane and ethane were performed at
111.66 K and 184.52 K respectively. \recheck{As it was discussed in~\cite{prx}, there is no requirement 
of a coarse-grained model that resembles the structural and thermodynamic properties of a full atomistic
model. It was shown numerically that the proper exchange of energy and molecules was independent from the 
molecular model used in the coarse-grained region, showing the convenience of GC-AdResS. In this work, a generic WCA potential was used in the 
coarse-grained region. The interaction potential between the coarse-grained particles is given by 
\begin{equation}
  U(r) = 4 \epsilon \left[\left(\frac{\sigma}{r}\right)^{12} - \left(\frac{\sigma}{r}\right)^{6}\right] + \epsilon,
  \quad
  r \leq 2^{1/6}\sigma. 
\end{equation}
The parameters $\sigma$ and $\epsilon$ were chosen such that the radial distribution functions of particles 
reproduce a liquid structure. For water molecule, the parameters used in this study are $\epsilon=0.65$~kJ/mol
and $\sigma=0.30$~nm. Table~\ref{cg} shows the WCA parameters for other molecules used in this work.
For interactions between solute and solvent, $\sigma$ values were obtained by 
averaging over the individual parameters.
The solute-solvent $\epsilon$ is the same as the solute-solute  $\epsilon$.
\\
}

@@

In all the simulations, a leap-frog stochastic dynamics integrator with a time step
of 2~fs and an inverse friction coefficient of 0.1~ps was used. All bond-lengths were constrained using the LINCS 
algorithm. \recheck{As discussed previously, a higher cut-off radius of $1.4$~nm has been used for van der Waals and Coulomb interactions,
in AdResS and full-atom simulations}. 
Electrostatic interactions  were calculated using the reaction-field term \cite{rf} with a dielectric 
permittivity of 54 for urea in SPC water \cite{urea}, 64.8 for TBA in SPC water \cite{nico}, 61 for other solutes in SPC
water, 19 for methanol and 46 for DMSO as the solvent \cite{vang}.

### 2014-05-20 writeDown/pub.jcp/resubmission.tex
update the values in the table. change small things

(1) Thermodynamic limit for the {atomistic and the coarse-grained region. (i.e. the number of molecules in both of the two
  regions are infinitely large, and the coarse-grained region is infinitely larger than the atomistic region)}.
% (1) Thermodynamic limit for the coarse-grained region (i.e. number of molecule very large).

@@

(1) Thermodynamic limit for the {atomistic and the coarse-grained region. (i.e. the number of molecules in both of the two
  regions are infinitely large, and the coarse-grained region is infinitely larger than the atomistic region)}.

@@

% \recheck{
%   The main purpose of the paper was to show the numerical accuracy of the theory, so we did not provide the theoretical derivation of
% }
% We have taken such a comment as a motivation to make an effort and finalize a derivation of the formula defined {\it ``weak''} by the referee. The derivation is presented as one of the results of this paper and has got its own section.
We have taken such a comment as a motivation to {provide the} derivation of the formula defined {\it ``weak''} by the referee. The derivation is presented as one of the results of this paper and has got its own section.
Although developed before the submission of this paper, this result was not presented, because the paper was intended to investigate only the numerical accuracy.

>>>>

(1) Thermodynamic limit for the {atomistic and the coarse-grained region. (i.e. the numbers of molecules in both of the two
  regions are infinitely large, and the coarse-grained region is infinitely larger than the atomistic region)}.
% (1) Thermodynamic limit for the coarse-grained region (i.e. number of molecule very large).

@@

(1) Thermodynamic limit for the {atomistic and the coarse-grained region. (i.e. the numbers of molecules in both of the two
  regions are infinitely large, and the coarse-grained region is infinitely larger than the atomistic region)}.

@@

% \recheck{
%   The main purpose of the paper was to show the numerical accuracy of the theory, so we did not provide the theoretical derivation of
% }
% We have taken such a comment as a motivation to make an effort and finalize a derivation of the formula defined {\it ``weak''} by the referee. The derivation is presented as one of the results of this paper and has got its own section.
We have taken such a comment as a motivation to {provide the} derivation of the formula defined {\it ``weak''} by the referee. The derivation is presented as one of the results of this paper and has got its own section.
Although developed before the submission of the manuscript, this result was not presented because the paper was intended to investigate only the numerical accuracy.
